---
title: "flat_additional.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(shiny)
library(purrr)
```

```{r development-1}
pkgload::load_all()
library(testthat)
library(shiny)
library(purrr)
```

See Boostrap documentation for more details:
https://getbootstrap.com/docs/5.1/components/carousel/

A carousel is a slideshow component for cycling through elements.

A carousel got some carousel items. Each item has is own body, images or text.

# Create carousel item

Inside a carousel item you can add images or text.
You can add a `is_active` param to the item to tell if the item is the active item (generaly the first item).

```{r function-carousel_item}
#' create a carousel item
#'
#' @param is_active is the carousel item active
#' @param ... content to display in the carousel body
#'
#' @return shiny.tag
#' @export
carousel_item <- function(is_active, ...) {
  tags$div(
    class = ifelse(isTRUE(is_active), "carousel-item active", "carousel-item"),
    ...
  )
}
```

```{r examples-carousel_item}
carousel_item(
  is_active = TRUE,
  tags$img(src = system.file(
    "app", "www", "templates", "thinkr", "assets", "logo.jpg",
    package = "signature"
  ))
)
```

```{r tests-carousel_item}
test_that("carousel_item works", {
  item_true <- carousel_item(is_active = TRUE, img(src = "..."))
  item_false <- carousel_item(is_active = FALSE, img(src = "..."))
  expect_true(inherits(item_true, "shiny.tag"))
  expect_snapshot(item_true)
  expect_snapshot(item_false)
})
```

# Create carousel indicator

Inside the carousel, we add indicators to switch between slides.
Used internal inside `carousel()`

```{r function-carousel_indicator}
#' create a carousel indicator
#'
#' @param id id of the carousel
#' @param carousel_item carousel_item()
#' @param pos carousel item position in the taglist
#'
#' @importFrom htmltools tagGetAttribute tagAppendAttributes
#'
#' @return shiny.tag
#' @export
carousel_indicator <- function(id, carousel_item, pos) {
  button <- tags$button(
    type = "button",
    `data-bs-target` = paste0("#", id),
    `data-bs-slide-to` = pos - 1,
    `aria-label` = paste0("Slide ", pos)
  )

  if (tagGetAttribute(carousel_item, "class") == "carousel-item active") {
    button <- tagAppendAttributes(button, class = "active")
    button <- tagAppendAttributes(button, `aria-current` = "true")
  }
  return(button)
}
```

```{r examples-carousel_indicator}
carousel_indicator(
  id = "indic",
  carousel_item = carousel_item(
    is_active = TRUE,
    tags$img(src = system.file(
      "app", "www", "templates", "thinkr", "assets", "logo.jpg",
      package = "signature"
    ))
  ),
  pos = 1
)
```

```{r tests-carousel_indicator}
test_that("carousel_indicator works", {
  indicator <- carousel_indicator(
    id = "indic",
    carousel_item = carousel_item(
      is_active = TRUE,
      tags$img(src = "...")
    ),
    pos = 1
  )
  expect_true(inherits(indicator, "shiny.tag"))
  expect_snapshot(indicator)
})
```

# Create carousel

Finally, you can create a carousel with `carousel()`

A carousel has a `tagList` of `carousel_items`.

```{r function-carousel}
#' create a carousel
#'
#' @param id id of the carousel for html
#' @param carousel_items a taglist of carousel_item()
#'
#' @importFrom purrr map2
#'
#' @return shiny.tag
#'
#' @export
carousel <- function(id, carousel_items) {
  carousel_indicators <- carousel_items %>%
    map2(
      seq_along(.),
      ~ carousel_indicator(id = id, carousel_item = .x, pos = .y)
    )

  tags$div(
    id = id,
    class = "carousel slide",
    `data-bs-ride` = "carousel",
    tags$div(
      class = "carousel-indicators",
      carousel_indicators
    ),
    tags$div(
      class = "carousel-inner",
      carousel_items
    ),
    tags$button(
      class = "carousel-control-prev",
      type = "button",
      `data-bs-target` = paste0("#", id),
      `data-bs-slide` = "prev",
      tags$span(
        class = "carousel-control-prev-icon",
        `aria-hidden` = "true"
      ),
      tags$span(
        class = "visually-hidden",
        "Previous"
      )
    ),
    tags$button(
      class = "carousel-control-next",
      type = "button",
      `data-bs-target` = paste0("#", id),
      `data-bs-slide` = "next",
      tags$span(
        class = "carousel-control-next-icon",
        `aria-hidden` = "true"
      ),
      tags$span(
        class = "visually-hidden",
        "Next"
      )
    )
  )
}
```

```{r examples-carousel}
carousel(
  id = "carouselExample",
  tagList()
)

carousel(
  id = "carouselExampleIndicators",
  carousel_item = tagList(
    carousel_item(
      is_active = TRUE,
      tags$img(src = system.file(
        "app", "www", "templates", "thinkr", "assets", "logo.jpg",
        package = "signature"
      ))
    ),
    carousel_item(
      is_active = FALSE,
      tags$img(src = system.file(
        "app", "www", "templates", "thinkr", "assets", "logo.jpg",
        package = "signature"
      ))
    )
  )
)
```

```{r tests-carousel}
test_that("accordion works", {
  acc <- accordion(id = "myaccordion", items = tagList())
  expect_true(inherits(acc, "shiny.tag"))
  expect_snapshot(acc)

  acc2 <- carousel(
    id = "carouselExampleIndicators",
    carousel_item = tagList(
      carousel_item(
        is_active = TRUE,
        tags$img(src = "...")
      ),
      carousel_item(
        is_active = FALSE,
        tags$img(src = "...")
      )
    )
  )
  expect_true(inherits(acc2, "shiny.tag"))
  expect_snapshot(acc2)
})
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_carousel.Rmd",
  vignette_name = "Create a carousel",
  check = FALSE
)
```

